
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "##>",
  tidy = FALSE,
  error = FALSE)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/r-lib/prettyunits/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-lib/prettyunits/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/r-lib/prettyunits/branch/main/graph/badge.svg)](https://app.codecov.io/gh/r-lib/prettyunits?branch=main)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/prettyunits)](https://CRAN.R-project.org/package=prettyunits)
<!-- badges: end -->

# prettyunits

The `prettyunits` package formats quantities in human readable form. Currently
time units and information (i.e. bytes) are supported.

## Installation

You can install the package from CRAN:

```{r eval = FALSE}
install.packages("prettyunits")
```

```{r}
library(prettyunits)
library(magrittr)
```

## Bytes

`pretty_bytes` formats number of bytes in a human readable way:

```{r}
pretty_bytes(1337)
pretty_bytes(133337)
pretty_bytes(13333337)
pretty_bytes(1333333337)
pretty_bytes(133333333337)
```

Here is a simple function that emulates the Unix `ls` command, with
nicely formatted file sizes:

```{r}
uls <- function(path = ".") {
  files <- dir(path)
  info <- files %>%
    lapply(file.info) %>%
    do.call(what = rbind)
  info$size <- pretty_bytes(info$size)
  df <- data.frame(d = ifelse(info$isdir, "d", " "),
	mode = as.character(info$mode), user = info$uname, group = info$grname,
    size = ifelse(info$isdir, "", info$size), modified = info$mtime, name = files)
  print(df, row.names = FALSE)
}
uls()
```

## Time intervals

`pretty_ms` formats a time interval given in milliseconds. `pretty_sec` does
the same for seconds, and `pretty_dt` for `difftime` objects. The optional
`compact` argument turns on a compact, approximate format.

```{r}
pretty_ms(c(1337, 13370, 133700, 1337000, 1337000000))
pretty_ms(c(1337, 13370, 133700, 1337000, 1337000000),
  compact = TRUE)
pretty_sec(c(1337, 13370, 133700, 1337000, 13370000))
pretty_sec(c(1337, 13370, 133700, 1337000, 13370000),
  compact = TRUE)

```

## Vague time intervals

`vague_dt` and `time_ago` formats time intervals using a vague format,
omitting smaller units. They both have three formats: `default`, `short` and `terse`.
`vague_dt` takes a `difftime` object, and `time_ago` works relatively to the
specified date.

```{r}
vague_dt(format = "short", as.difftime(30, units = "secs"))
vague_dt(format = "short", as.difftime(14, units = "mins"))
vague_dt(format = "short", as.difftime(5, units = "hours"))
vague_dt(format = "short", as.difftime(25, units = "hours"))
vague_dt(format = "short", as.difftime(5, units = "days"))
```

```{r}
now <- Sys.time()
time_ago(now)
time_ago(now - as.difftime(30, units = "secs"))
time_ago(now - as.difftime(14, units = "mins"))
time_ago(now - as.difftime(5, units = "hours"))
time_ago(now - as.difftime(25, units = "hours"))
```

## Rounding

`pretty_round()` and `pretty_signif()` preserve trailing zeros.

```{r}
pretty_round(1, digits=6)
pretty_signif(c(99, 0.9999), digits=3)
```

## p-values

`pretty_p_value()` rounds small p-values to indicate less than significance
level for small values.

```{r}
pretty_p_value(c(0.05, 0.0000001, NA))
```
